\documentclass{letter}

\usepackage{xspace}
\newcommand{\CEU}{\textsc{C\'{e}u}\xspace}

\signature{Anonymous Author}
%\signature{Prof. Francisco Sant'Anna}
%\address{Department of Computer Science \\ Rio de Janeiro State University \\ Brazil}
\date{April 27, 2018}

\begin{document}

\begin{letter}{Elsevier Computer and Graphics Journal}

\opening{Dear Editor of C\&G:}

I am submitting a paper for the special issue \emph{SBGames 2018} entitled
``Structured Synchronous Reactive Programming for Game Development ---
Case Study: On Rewriting Pingus from C++ to \CEU''.
I declare that the paper has not been published or submitted elsewhere.
I also declare that the work is an original case study that is not based on
previous work from myself or others.
I am the only author of the paper.

The paper presents a qualitative case study of rewriting the video game Pingus
from C++ to the structured synchronous reactive language \CEU.
%
\CEU supports reactive control-flow primitives that helps describing complex
interactions in the game logic more concisely.
%
We show gains in productivity for six behaviors in Pingus through a qualitative
analysis of the proposed implementations in \CEU in comparison to the originals
in C++.
%
We also categorize the behaviors in four recurrent control-flow patterns that
likely apply to most games.

The paper is in the scope of ``research and applications of interactive
computer graphics'' since it proposes new control abstractions to model
real-time interactions between graphical entities in a video game.

In summary, these are the main contributions of the paper:
%
\begin{itemize}
\item Qualitative case study of rewriting the game Pingus from C++ to \CEU.
\item Gains in productivity for six behaviors in the game.
\item Categorization of the behaviors in four recurrent control-flow patterns.
\end{itemize}

\closing{Yours Sincerely,}

\ps

\end{letter}
\end{document}
